---
title: "a3"
author: "Haozhe Cui"
data : "2/22/2021"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
data <- read.csv("incarceration_trends.csv")

```

## Introduction 
One of the sharpest manifestations of racism in the United States is its prison system. By exploring incarceration_trends data, we can use R to analyze whether inequality occurs between black and white. In this practice, I will focus on the jail and prison populations to explore this phenomenon.

In my summary statistic page, I first calculate the total population between 2008 to 2018 to use the most recent data information to analyze. Then, by calculating the mean of some of the population in each state, I get the five most populated states between 2008 to 2018, and they are VT, WI, WY, WA, and WV. I want to use these top 5 states to analyze because they can highlight the most obvious question I want. Finally, by calculating the ratio between the white and black population in the jail and prison in these five states between 2008 to 2018, I find the black percentage in the jail and prison is much higher than the white. (jail_ratio between black and white: 359.2596 and inf, prison_ration between black and white:192.2482 and inf)


## Chart 1
```{r, echo=FALSE, message=FALSE}
source("chart1.R")
chart1

```
This chart was intended to show the trend of black population in prison between 1970 to 2020 to explore whether the trend of the increase of the black prison population presents in progressive way. Also, I put two lines to show the  the 10 times of mean between prison population of the black and white to present a contrast of prison population of white and mean. Based on these two parts of plots, we find that the black prison population rapidly increase after 1984 and maintain a relevant high prison population. On the other hand, the mean of the black population(black lines) is larger than the mean of white (blue line).
## chart 2

```{r, echo=FALSE, message=FALSE}
source("chart2.R")
chart2

```
This chart is intended to demonstrate the contrast of the prison population of white and black in four primary regions to take a closer look at the numerical differences between them. From the graph, we can see that the overall population of black is much higher than the white in these four regions between 1970 to 2020. 

## Chart 3
This chart is intended to show the distribution of total jail population in Washington state. By demonstrating the distribution, we could efficiently focus on places where have the most total jail population to effectively analyze the existence of ineuqaility between black and white.
```{r, echo=FALSE, message=FALSE}
source("chart3.R")
chart3
```